*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Name all R chunks;

```{r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(microbenchmark, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "*",
        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
        "* and *",
        tail(x, n = 1),
        "*"),
      collapse = "")} )

@@

```{r, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```

@@

```{r, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
```

@@

```{r, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
```

@@

```{r, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
```

@@

```{r, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
```

@@

```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
```

```{r, echo = FALSE}
max_PPR <- read.delim(
    file.path(tmpDir,"inputTable.txt"),
    check.names = FALSE) %>%
  flippant:::calculate_ppr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
```

```{r, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

```{r, echo = FALSE, cache = TRUE}

>>>>

```{r setting_up_r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(microbenchmark, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "*",
        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
        "* and *",
        tail(x, n = 1),
        "*"),
      collapse = "")} )

@@

```{r noeval_demonstrate_installation, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```

@@

```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
```

@@

```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
```

@@

```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
```

@@

```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
```

@@

```{r noeval_demonstrate_traces, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
```

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
```

```{r calculate_pprs, echo = FALSE}
max_PPR <- read.delim(
    file.path(tmpDir,"inputTable.txt"),
    check.names = FALSE) %>%
  flippant:::calculate_ppr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
```

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

```{r analysis_timing, echo = FALSE, cache = TRUE}
